Constraints to Validate RDF Data Quality on

### 2015-09-11 paper/IEEE-ICSC-2016/technical-reports/IEEE-ICSC-2016-constraints.tex
TRs

\begin{document}
\renewcommand{\arraystretch}{1.3}
%
%
\title{RDF Constraints to Validate}
\subtitle{Rectangular Data and Metadata on Person-Level Data, Aggregated Data, Thesauri, and Statistical Classifications}

@@

\begin{abstract}
To ensure high quality of and trust in both metadata and data, their representation in RDF must satisfy certain criteria - specified in terms of RDF constraints.
From 2012 to 2015 together with other Linked Data community members and experts from the social, behavioural, and economic sciences (\emph{SBE}), we developed diverse vocabularies to represent \emph{SBE} metadata and rectangular data in RDF.
The \emph{DDI-RDF Discovery Vocabulary (Disco)} 
is designed to support the dissemination, management,
and reuse of person-level data, i.e., data about individuals, households, and businesses, collected in form of responses to studies and archived for research purposes.
The \emph{RDF Data Cube Vocabulary (Data Cube)} is a W3C recommendation for expressing \emph{data cubes}, i.e. multi-dimensional aggregate data. 
\emph{Physical Data Description (PHDD)} is a vocabulary to model data in rectangular format. 
The data could either be represented in records with character-separated values (\emph{CSV}) or fixed length. 
The \emph{Simple Knowledge Organization System (SKOS)} is a vocabulary to build knowledge organization systems such as thesauri, classification schemes, and taxonomies.
\emph{XKOS} is a SKOS extension to describe formal statistical classifications.

In this paper, we describe RDF constraints to validate metadata on person-level data (\emph{Disco}), aggregated data (\emph{Data Cube}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) and to validate rectangular data (\emph{PHDD}).
We assign RDF constraints to RDF constraint types either corresponding to RDF validation requirements or to data model specific constraint types.
This technical report is updated continuously as modifying, adding, and deleting constraints remains ongoing work.

\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Thesauri, SKOS, Rectangular Data, Statistical Classifications, XKOS, Linked Data, Semantic Web}
\end{abstract}

@@

Bosch and Eckert initiated a comprehensive database\footnote{Publicly available at \url{http://purl.org/net/rdf-validation}.} on RDF validation requirements to collect case studies, use cases, and requirements \cite{BoschEckert2014}. 
It is continuously updated and used to evaluate and to compare various existing solutions for RDF constraint formulation and validation. 
Requirements are classified to provide a high-level view on different solutions and to facilitate a better understanding of the problem domain.
Bosch et al. identified in total 76 requirements to formulate RDF constraints; each of them corresponding to a constraint type. 
They recently published a technical report\footnote{Available at: \url{http://arxiv.org/abs/1501.03933}} in which they explain each requirement (constraint type) in detail and give examples for each (represented by listed constraint languages) \cite{BoschNolleAcarEckert2015}.
Where appropriate constraint types are related to complementary requirements of the RDF validation requirements database.

We distinguish two validation types:
(1) \emph{Content-Driven Validation} $\mathcal{C}_{C}$ contains the set of constraints ensuring that the data is consistent with the intended syntax, semantics, and integrity of given data models.
(2) \emph{Technology-Driven Validation} $\mathcal{C}_{T}$ includes the set of constraints which can be generated automatically out of data models, such as cardinality restrictions, universal and existential quantifications, domains, and ranges.
We determined the default \emph{severity level} (corresponds to requirement \emph{R-158}) for each constraint to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from $\mathcal{SL}_{0}$ (informational) via $\mathcal{SL}_{1}$ (warning) to $\mathcal{SL}_{2}$ (error). 
Although we provide default severity levels for each constraint, users should be able to specify severity levels of constraints they need to validate for their individual use cases, i.e., users should be able to define use case specific severity levels for constraints.

The following two sections encompass RDF constraints classified as constraint types either corresponding to RDF validation requirements (section \ref{RDF-validation-requirements-constraint-types}) or data model specific constraint types (section \ref{data-model-specific-constraint-types}).
Constraint types marked with an asterisk (*) can be used as OWL 2 axioms. Thus, reasoners may be used prior to the validation to infer implicit triples which may resolve or cause constraint violations.
$\mathcal{C}_{T}$ constraint types are marked with the superscript\textsuperscript{B}.
As $\mathcal{C}_{T}$ and $\mathcal{C}_{C}$ are disjoint sets, $\mathcal{C}_{C}$ constraint types are not explicitly marked.

%\section{RDF Constraints to Validate Metadata and Data}

\section{RDF Constraint Types Corresponding to RDF Validation Requirements}
\label{RDF-validation-requirements-constraint-types}

\subsection{Subsumption*\textsuperscript{B}}

@@

\subsection{Class Equivalence*\textsuperscript{B}}

@@

\subsection{Sub Properties*\textsuperscript{B}}

@@

\subsection{Property Domains*\textsuperscript{B}}

@@

\subsection{Property Ranges*\textsuperscript{B}}

@@

\subsection{Inverse Object Properties*\textsuperscript{B}}

@@

\subsection{Symmetric Object Properties*\textsuperscript{B}}

@@

\subsection{Asymmetric Object Properties*\textsuperscript{B}}

@@

\subsection{Reflexive Object Properties*\textsuperscript{B}}

@@

\subsection{Irreflexive Object Properties*\textsuperscript{B}}

@@

\subsection{Class-Specific Irreflexive Object Properties*\textsuperscript{B}}

@@

\subsection{Disjoint Properties\textsuperscript{B}}

@@

\subsection{Disjoint Classes\textsuperscript{B}}

@@

\subsection{Context-Specific Property Groups\textsuperscript{C}}

@@

\subsection{Context-Specific Inclusive OR of Properties\textsuperscript{C}}

@@

\subsection{Context-Specific Inclusive OR of Property Groups\textsuperscript{C}}

@@

\subsection{Recursive Queries\textsuperscript{C}}

@@

\subsection{Individual Inequality\textsuperscript{B}}

@@

\subsection{Equivalent Properties*\textsuperscript{B}}

@@

\subsection{Property Assertions\textsuperscript{B}}

@@

\subsection{Data Property Facets\textsuperscript{S}}

@@

\subsection{Literal Pattern Matching\textsuperscript{S}}

@@

\subsection{Negative Literal Pattern Matching\textsuperscript{S}}

@@

\subsection{Object Property Paths*\textsuperscript{B}}

@@

\subsection{Intersection*\textsuperscript{B}}

@@

\subsection{Disjunction*\textsuperscript{B}}

@@

\subsection{Negation*\textsuperscript{B}}

@@

\subsection{Existential Quantifications*\textsuperscript{B}}

@@

\subsection{Universal Quantifications*\textsuperscript{B}}

@@

\subsection{Minimum Unqualified Cardinality Restrictions*\textsuperscript{B}}

@@

\subsection{Minimum Qualified Cardinality Restrictions*\textsuperscript{B}}

@@

\subsection{Maximum Unqualified Cardinality Restrictions*\textsuperscript{B}}

@@

\subsection{Maximum Qualified Cardinality Restrictions*\textsuperscript{B}}

@@

\subsection{Exact Unqualified Cardinality Restrictions*\textsuperscript{B}}

@@

\subsection{Exact Qualified Cardinality Restrictions*\textsuperscript{B}}

@@

\subsection{Transitive Object Properties*\textsuperscript{B}}

@@

\subsection{Context-Specific Exclusive OR of Properties\textsuperscript{C}}

@@

\subsection{Context-Specific Exclusive OR of Property Groups\textsuperscript{C}}

@@

\subsection{Allowed Values\textsuperscript{B}}

@@

\subsection{Not Allowed Values\textsuperscript{B}}

@@

\subsection{Literal Ranges\textsuperscript{S}}

@@

\subsection{Negative Literal Ranges\textsuperscript{S}}

@@

\subsection{Required Properties\textsuperscript{B}}

@@

\subsection{Optional Properties\textsuperscript{B}}

@@

\subsection{Repeatable Properties\textsuperscript{B}}

@@

\subsection{Negative Property Constraints\textsuperscript{S}}

@@

\subsection{Individual Equality*\textsuperscript{B}}

@@

\subsection{Functional Properties*\textsuperscript{B}}

@@

\subsection{Inverse-Functional Properties*\textsuperscript{B}}

@@

\subsection{Value Restrictions*\textsuperscript{B}}

@@

\subsection{Self Restrictions*\textsuperscript{B}}

@@

\subsection{Primary Key Properties*\textsuperscript{B}}

@@

\subsection{Class-Specific Property Range*\textsuperscript{B}}

@@

\subsection{Class-Specific Reflexive Object Properties*\textsuperscript{B}}

@@

\subsection{Membership in Controlled Vocabularies\textsuperscript{S}}

@@

\subsection{IRI Pattern Matching\textsuperscript{S}}

@@

\subsection{Literal Value Comparison\textsuperscript{S}}

@@

\subsection{Ordering\textsuperscript{C}}

@@

\subsection{Validation Levels\textsuperscript{S}}

@@

\subsection{String Operations\textsuperscript{S}}

@@

\subsection{Context-Specific Valid Classes\textsuperscript{B}}

@@

\subsection{Context-Specific Valid Properties\textsuperscript{B}}

@@

\subsection{Default Values*\textsuperscript{S}}

@@

\subsection{Mathematical Operations\textsuperscript{C}}

@@

\subsection{Language Tag Matching\textsuperscript{S}}

@@

\subsection{Language Tag Cardinality\textsuperscript{S}}

@@

\subsection{Whitespace Handling\textsuperscript{S}}

@@

\subsection{HTML Handling\textsuperscript{S}}

@@

\subsection{Conditional Properties\textsuperscript{C}}

@@

\subsection{Recommended Properties\textsuperscript{S}}

@@

\subsection{Handle RDF Collections\textsuperscript{C}}

@@

\subsection{Value is Valid for Datatype\textsuperscript{B}}

@@

\subsection{Use Sub-Super Relations in Validation\textsuperscript{B}}

\footnote{\emph{R-224-USE-SUB-SUPER-RELATIONS-IN-VALIDATION}}

@@

\subsection{Cardinality Shortcuts*\textsuperscript{B}}

@@

\subsection{Aggregations\textsuperscript{C}}

@@

\subsection{Provenance\textsuperscript{S}}

@@

\section{Data Model Specific RDF Constraint Types}
\label{data-model-specific-constraint-types}

\subsection{Comparison\textsuperscript{C}}

@@

\subsection{Data Model Consistency\textsuperscript{C}}
Is the data consistent with the intended semantics of the data model?
Such validation rules ensure the integrity of the data according to the data model.

@@

\subsection{Structure\textsuperscript{C}}

@@

\subsection{Labeling and Documentation\textsuperscript{S}}

@@

\subsection{Vocabulary\textsuperscript{B}}
Vocabularies should not invent any new terms or use deprecated elements.

@@

\subsection{HTTP URI Scheme Violation\textsuperscript{S}}

@@

\bibliography{../../literature/literature}{}
\bibliographystyle{plain}
\setcounter{tocdepth}{1}
%\listoftodos
\end{document}

>>>>

\begin{document}
\renewcommand{\arraystretch}{1.3}
%
%
\title{Constraints to Validate RDF Data Quality on}
\subtitle{Common Vocabularies in the Social, Behavioral, and Economic Sciences}

@@

\begin{abstract}
To ensure high quality of and trust in both metadata and data, their representation in RDF must satisfy certain criteria - specified in terms of RDF constraints.
From 2012 to 2015 together with other Linked Data community members and experts from the social, behavioral, and economic sciences (\emph{SBE}), we developed diverse vocabularies to represent \emph{SBE} metadata and rectangular data in RDF.

The \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)} 
is designed to support the dissemination, management,
and reuse of unit-record data, i.e., data about individuals, households, and businesses, collected in form of responses to studies and archived for research purposes.
The \emph{RDF Data Cube Vocabulary (QB)} is a W3C recommendation for expressing \emph{data cubes}, i.e. multi-dimensional aggregate data and its metadata. 
\emph{Physical Data Description (PHDD)} is a vocabulary to model data in rectangular format, i.e., tabular data. 
The data could either be represented in records with character-separated values (\emph{CSV}) or fixed length. 
The \emph{Simple Knowledge Organization System (SKOS)} is a vocabulary to build knowledge organization systems such as thesauri, classification schemes, and taxonomies.
\emph{XKOS} is a SKOS extension to describe formal statistical classifications.

In this paper, we describe RDF constraints to validate metadata on unit-record data (\emph{DDI-RDF}), aggregated data (\emph{QB}), thesauri (\emph{SKOS}), and statistical classifications (\emph{XKOS}) and to validate tabular data (\emph{PHDD}) - all of them represented in RDF. We classified these constraints according to the severity of occurring constraint violations.
This technical report is updated continuously as modifying, adding, and deleting constraints remains ongoing work.

\keywords{RDF Validation, RDF Constraints, DDI-RDF Discovery Vocabulary, RDF Data Cube Vocabulary, Thesauri, SKOS, Tabular Data, Statistical Classifications, Linked Data, Semantic Web}
\end{abstract}

@@

For constraint formulation and RDF data validation, several languages exist or are currently developed. \emph{Shape Expressions (ShEx)}, \emph{Resource Shapes (ReSh)}, \emph{Description Set Profiles (DSP)}, \emph{OWL 2}, the \emph{SPARQL Inferencing Notation (SPIN)}, and \emph{SPARQL} are the six most promising and widely used constraint languages. OWL 2 is used as a constraint language under the closed-world and unique name assumptions. The W3C currently develops \emph{SHACL}, an RDF vocabulary for describing RDF graph structures. With its direct support of validation via SPARQL, SPIN is very popular and certainly plays an important role for future developments in this field. It is particularly interesting as a means to validate arbitrary constraint languages by mapping them to SPARQL \cite{BoschEckert2014-2}. Yet, there is no clear favorite and none of the languages is able to meet all requirements raised by data practitioners. Further research and development therefore is needed.

In 2013, the W3C organized the RDF Validation Workshop,\footnote{\url{http://www.w3.org/2012/12/rdf-val/}} 
where experts from industry, government, and academia discussed first use cases for constraint formulation and RDF data validation.
In 2014, two working groups on RDF validation have been established to develop a language to express constraints on RDF data: 
the \emph{W3C RDF Data Shapes Working Group}\footnote{\url{http://www.w3.org/2014/rds/charter}} (33 participants of 19 organizations) and the \emph{DCMI RDF Application Profiles Task Group}\footnote{\url{http://wiki.dublincore.org/index.php/RDF-Application-Profiles}} (29 people of 22 organizations) which among others bundles the requirements of data institutions of the cultural heritage sector and the \emph{social, behavioral, and economic (SBE)} sciences and represents them in the W3C group.

Within the DCMI task group, a collaboratively curated database of RDF validation requirements\footnote{Online available at: \url{http://purl.org/net/rdf-validation}} has been created which contains the findings of the working groups based on various case studies provided by data institutions \cite{BoschEckert2014}. It is publicly available and open for further contributions.
The database connects requirements to use cases, case studies, and implementations and forms the basis of this paper. 
We distinguish 81 requirements to formulate constraints on RDF data; 
each of them corresponding to a constraint type.

In this paper, we collected constraints for commonly used vocabularies in the SBE domain (see Section \ref{sbe-vocabularies}), either from the vocabularies themselves or from domain and data experts, in order to gain a better understanding about the role of certain requirements for data quality and to direct the further development of constraint languages. 
We let the experts classify the constraints according to the severity of their violation.

\section{Common Vocabularies in SBE Sciences}
\label{sbe-vocabularies}

We took all well-established and newly developed SBE vocabularies into account and defined constraints for three vocabularies commonly used in the SBE sciences which are briefly introduced in the following. We analyzed actual data according to constraint violations, as for these vocabularies large data sets are already published.

SBE sciences require high-quality data for their empirical research. For more than a decade, members of the SBE community have been developing and using a
metadata standard, composed of almost twelve hundred metadata fields, known as the \emph{Data Documentation Initiative (DDI)}, \footnote{\url{http://www.ddialliance.org/Specification/}}
an XML format to disseminate, manage,
and reuse data collected and archived for research \cite{Vardigan2008}. 
In XML, the definition of schemas containing constraints and the validation of data according to these constraints is commonly used to ensure a certain level of data quality.
With the rise of the Web of Data, data professionals and institutions are very interested in having their data be discovered and used by publishing their data directly in RDF or at least publish accurate metadata about their data to facilitate data integration. Therefore, not only established vocabularies like SKOS are used; 
recently, members of the SBE and Linked Data community developed with the \emph{DDI-RDF Discovery Vocabulary (DDI-RDF)}\footnote{\url{http://rdf-vocabulary.ddialliance.org/discovery.html}} a means to expose \emph{DDI} metadata as Linked Data.

The data most often used in research within SBE sciences is \emph{unit-record data}, i.e., data collected about individuals, businesses, and households, in form of responses to studies or taken from administrative registers such as hospital records, registers of births and deaths. A \emph{study} represents the process by which a data set was generated or collected. The range of unit-record data is very broad - including census, education, health data and business, social, and labor force surveys. This type of research data is held within data archives or data libraries after it has been collected, so that it may be reused by future researchers. By its nature, unit-record data is highly confidential and access is often only permitted for qualified researchers who must apply for access. Researchers typically represent their results as aggregated data in form of multi-dimensional tables with only a few columns: so-called \emph{variables} such as \emph{sex} or \emph{age}. Aggregated data, which answers particular research questions, is derived from unit-record data by statistics on groups or aggregates such as frequencies and arithmetic means. The purpose of publicly available aggregated data is to get a first overview and to gain an interest in further analyses on the underlying unit-record data. For more detailed analyses, researchers refer to unit-record data including additional variables needed to answer subsequent research questions.

\emph{Formal childcare} is an example of an aggregated variable which captures the measured availability of childcare services in percent over the population in European Union member states by 
the dimensions \emph{year}, \emph{duration}, \emph{age} of the child, and \emph{country}.
Variables are constructed out of values (of one or multiple datatypes) and/or code lists.
The variable \emph{age}, e.g., may be represented by values of the datatype \emph{xsd:nonNegativeInteger} or by a code list of age clusters (e.g., '0 to 10' and '11 to 20'). 
The \emph{RDF Data Cube Vocabulary (QB)}\footnote{http://www.w3.org/TR/vocab-data-cube/} is a W3C recommendation for representing \emph{data cubes}, i.e., multi-dimensional aggregated data, in RDF \cite{Cyganiak2010}. 
%QB represents metadata on multi-dimensional aggregate data in two files: a \emph{qb:DataSet} and a \emph{qb:DataStructureDefinition}.
A \emph{qb:DataStructureDefinition} contains metadata of the data collection.
The variable \emph{formal childcare} is modeled as \emph{qb:measure}, since it stands for what has been measured in the data collection.
\emph{Year}, \emph{duration}, \emph{age}, and \emph{country} are \emph{qb:dimensions}.
Data values, i.e., the availability of childcare services in percent over the population, are collected in a \emph{qb:DataSet}. 
Each data value is represented inside a \emph{qb:Observation} which contains values for each dimension. 
%(e.g., the year in which \emph{formal childcare} has been determined).
%\ke{Wieso springt das von einer sehr knappen Einführung direkt zu konkreten (beliebigen?) Variablen? Ich möchte wissen, wofür QB benutzt wird und gerne ein konkretes %Beispiel sehen, um mir einen Data Cube vorstellen zu können.}\tb{hmm, ich halte das beispiel für ein knappes und verständliches beipsiel wie eine tabelle in qb dargestellt wird / es ist auch der link enthalten zu der tabelle von eurostat}

For more detailed analyses we refer to the underlying unit-record data. The aggregated variable \emph{formal childcare} is calculated on the basis of six unit-record variables (i.a., \emph{Education at pre-school}) for which detailed metadata is given (i.a., code lists) enabling researchers to replicate the results shown in aggregated data tables.
\emph{DDI-RDF} is used to represent metadata on unit-record data in RDF.
%The series (\emph{DDI-RDF:StudyGroup}) \emph{EU-SILC} contains one study (\emph{DDI-RDF:Study}) for each year (\emph{dcterms:temporal}) of data collection.   
%\emph{dcterms:spatial} points to the countries for which the data has been collected.
The study (\emph{disco:Study}) for which the unit-record data has been collected 
%\emph{EU-SILC 2011} 
contains eight data sets (\emph{disco:LogicalDataSet})
including variables (\emph{disco:Variable}) like the six ones needed to calculate the variable \emph{formal childcare}.
%Metadata on unit-record data enables researchers to investigate further research questions based on promising findings of other researchers in form of aggregated data.
%One common research question is ,e.g., the comparison of variables like 
%\emph{formal childcare} between countries, for which the variable is collected within the context of an individual study, and other European or non European countries (e.g. OSCE).

The \emph{Simple Knowledge Organization System (SKOS)} is reused to a large extend to build SBE vocabularies.
The codes of the variable \emph{Education at pre-school} are modeled as \emph{skos:Concepts} and 
a \emph{skos:OrderedCollection} organizes them in a particular order within a \emph{skos:memberList}.
A variable may be associated with a theoretical concept (\emph{skos:Concept}) and \emph{skos:narrower} builds the hierarchy of theoretical concepts within a \emph{skos:ConceptScheme} of a study.
The variable \emph{Education at pre-school} is assigned to the theoretical concept \emph{Child Care} which is a narrower concept of the top concept \emph{Education}.
Controlled vocabularies (\emph{skos:ConceptScheme}), serving as extension and reuse mechanism,
organize types (\emph{skos:Concept}) of descriptive statistics (\emph{disco:SummaryStatistics}) like minimum, maximum, and arithmetic mean.

\section{Classification of RDF Constraints according to the Severity of Constraint Violations}

A concrete constraint is instantiated from one of the 81 constraint types and is defined for a specific vocabulary.
It does not make sense to determine the severity of constraint violations of an entire constraint type,
as the severity depends on the individual context and vocabulary.
%as the violation of one constraint may be severe,
%whereas, the violation of another constraint of the same type may be minor.
SBE experts determined the default \emph{severity level}\footnote{The possibility to define severity levels in vocabularies is in itself a requirement (\emph{R-158}).} for each constraint to indicate how serious the violation of the constraint is. We use the classification system of log messages in software development like \emph{Apache Log4j 2} \cite{Apache-2015}, the \emph{Java Logging API},\footnote{\url{http://docs.oracle.com/javase/7/docs/api/java/util/logging/Level.html}} and the \emph{Apache Commons Logging API}\footnote{\url{http://commons.apache.org/proper/commons-logging/}} as many data practitioners also have experience in software development and software developers intuitively understand these levels. We simplify this commonly accepted classification system and distinguish the three severity levels (1) \emph{informational}, (2) \emph{warning}, and (3) \emph{error}.
%According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt... mein vorschlag von eben kann das komplett ersetzen.}
%\begin{itemize}
	%\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
	%\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
	%\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
%\end{itemize}
Violations of \emph{informational} constraints point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
%They are not seen as serious errors.
\emph{Warnings} are syntactic or semantic problems which typically should not lead to an abortion of data processing.
\emph{Errors}, in contrast, are syntactic or semantic errors which should cause the abortion of data processing. 
%Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
%Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
%Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
Although we provide default severity levels for each constraint, validation environments should enable users to adapt the severity levels of constraints according to their individual needs.

\section{RDF Constraints by RDF Constraint Type}

\subsection{Subsumption}

@@

\subsection{Class Equivalence}

@@

\subsection{Sub Properties}

@@

\subsection{Property Domains}

@@

\subsection{Property Ranges}

@@

\subsection{Inverse Object Properties}

@@

\subsection{Symmetric Object Properties}

@@

\subsection{Asymmetric Object Properties}

@@

\subsection{Reflexive Object Properties}

@@

\subsection{Irreflexive Object Properties}

@@

\subsection{Class-Specific Irreflexive Object Properties}

@@

\subsection{Disjoint Properties}

@@

\subsection{Disjoint Classes}

@@

\subsection{Context-Specific Property Groups}

@@

\subsection{Context-Specific Inclusive OR of Properties}

@@

\subsection{Context-Specific Inclusive OR of Property Groups}

@@

\subsection{Recursive Queries}

@@

\subsection{Individual Inequality}

@@

\subsection{Equivalent Properties}

@@

\subsection{Property Assertions}

@@

\subsection{Data Property Facets}

@@

\subsection{Literal Pattern Matching}

@@

\subsection{Negative Literal Pattern Matching}

@@

\subsection{Object Property Paths}

@@

\subsection{Intersection}

@@

\subsection{Disjunction}

@@

\subsection{Negation}

@@

\subsection{Existential Quantifications}

@@

\subsection{Universal Quantifications}

@@

\subsection{Minimum Unqualified Cardinality Restrictions}

@@

\subsection{Minimum Qualified Cardinality Restrictions}

@@

\subsection{Maximum Unqualified Cardinality Restrictions}

@@

\subsection{Maximum Qualified Cardinality Restrictions}

@@

\subsection{Exact Unqualified Cardinality Restrictions}

@@

\subsection{Exact Qualified Cardinality Restrictions}

@@

\subsection{Transitive Object Properties}

@@

\subsection{Context-Specific Exclusive OR of Properties}

@@

\subsection{Context-Specific Exclusive OR of Property Groups}

@@

\subsection{Allowed Values}

@@

\subsection{Not Allowed Values}

@@

\subsection{Literal Ranges}

@@

\subsection{Negative Literal Ranges}

@@

\subsection{Required Properties}

@@

\subsection{Optional Properties}

@@

\subsection{Repeatable Properties}

@@

\subsection{Negative Property Constraints}

@@

\subsection{Individual Equality}

@@

\subsection{Functional Properties}

@@

\subsection{Inverse-Functional Properties}

@@

\subsection{Value Restrictions}

@@

\subsection{Self Restrictions}

@@

\subsection{Primary Key Properties}

@@

\subsection{Class-Specific Property Range}

@@

\subsection{Class-Specific Reflexive Object Properties}

@@

\subsection{Membership in Controlled Vocabularies}

@@

\subsection{IRI Pattern Matching}

@@

\subsection{Literal Value Comparison}

@@

\subsection{Ordering}

@@

\subsection{Validation Levels}

@@

\subsection{String Operations}

@@

\subsection{Context-Specific Valid Classes}

@@

\subsection{Context-Specific Valid Properties}

@@

\subsection{Default Values}

@@

\subsection{Mathematical Operations}

@@

\subsection{Language Tag Matching}

@@

\subsection{Language Tag Cardinality}

@@

\subsection{Whitespace Handling}

@@

\subsection{HTML Handling}

@@

\subsection{Conditional Properties}

@@

\subsection{Recommended Properties}

@@

\subsection{Handle RDF Collections}

@@

\subsection{Value is Valid for Datatype}

@@

\subsection[Use Sub-Super Relations in Validation] {Use Sub-Super Relations in Validation\footnote{\emph{R-224-USE-SUB-SUPER-RELATIONS-IN-VALIDATION}}}

%\subsection{Use Sub-Super Relations in Validation{\footnote{\emph{R-224-USE-SUB-SUPER-RELATIONS-IN-VALIDATION}}}}

@@

\subsection{Cardinality Shortcuts}

@@

\subsection{Aggregations}

@@

\subsection{Provenance}

@@

\subsection{Comparison}
\setcounter{subsection}{76}

@@

\subsection{Data Model Consistency}
Is the data consistent with the intended semantics of the data model?
Such validation rules ensure the integrity of the data according to the data model.

@@

\subsection{Structure}

@@

\subsection{Labeling and Documentation}

@@

\subsection{Vocabulary}
Vocabularies should not invent any new terms or use deprecated elements.

@@

\subsection{HTTP URI Scheme Violation}

@@

\section{Conclusion}

We identified and published by today 81 types of constraints  that are required by various stakeholders for data applications.
In close collaboration with several domain experts for the social, behavioral, and economic sciences (SBE), we formulated constraints on common SBE vocabularies and classified them according to their severity level.

\bibliography{../../../literature/literature}{}
\bibliographystyle{plain}
\setcounter{tocdepth}{1}
%\listoftodos
\end{document}
